Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex
Fix BIB. Few comments to Benchmarks.

\section{Benchmarks}
\label{sec:benchmarks}
In this section we present numerical results on several benchmark problems. At first we shall compare 
the effectivity of our fundamental algorithms for intersections with other approaches.

@@

\vspace{2ex}
\begin{minipage}{\textwidth}
    \centering
    \hspace{-30pt}
  \begin{minipage}[b]{0.44\textwidth}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}[b]{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
    \end{tabular}
    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
                      Only 2D-3D case considered.
    \label{tab:fundamental_flops}
    \notePE{comment on different strategies}}
  \end{minipage}
  \hfil
  \begin{minipage}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}

    \captionof{figure}{Effectivity of our algorithms using \plucker coordinates in comparison to \notePE{***}.
                         One can see 1D-3D case on the left, 2D-3D on the right.}
    \label{fig:fundamental_speed}
    \end{minipage}
\end{minipage}
\vspace{2ex}

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

@@

\begin{table}[!htb]
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}}
        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
        BIH(AABB) & AABB & BIH(AABB) \\
        AFront & AFront & ---
    \end{tabular}
    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.}
    \label{tab:search_algorithms}
\end{table}

>>>>

\section{Benchmarks}
\label{sec:benchmarks}
In this section we present numerical results on several benchmark problems. At first we shall compare 
the effectivity of our fundamental algorithms for intersections with other approaches.
\noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
\noteJB{We compare just against NGH which we should briefly describe. Neither of the algorithms is optimized. The new one deals correctly with special cases and provides 
barycentric coordinates (so more work for less time).}
\noteJB{Also write little about Flow123d here. The language etc.}

@@

\vspace{2ex}
\begin{minipage}{\textwidth}
    \centering
    \hspace{-30pt}
  \begin{minipage}[b]{0.44\textwidth}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}[b]{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
    \end{tabular}
    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
                      Only 2D-3D case considered.}
    \label{tab:fundamental_flops}
    \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
  \end{minipage}
  \hfil
  \begin{minipage}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}

    \captionof{figure}{Efficiency of \plucker approach compared to the legacy NGH code.}
    \label{fig:fundamental_speed}
    \end{minipage}
\end{minipage}
\vspace{2ex}

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}NGH. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

@@

\begin{table}[!htb]
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}}
        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
        BIH(AABB) & AABB & BIH(AABB) \\
        AFront & AFront & ---
    \end{tabular}
    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
    \noteJB{Just in the text. Possibly use different name for variants.}}
    \label{tab:search_algorithms}
\end{table}
